Inside Out: Externalizing Assumptions in Data Analysis as Validation Checks

### 2025-10-02 index.qmd
minor revision

>>>>

# Supplementary material {.unnumbered}

The supplementary materials include a full script of the examples in the paper (`index.R`) and its output (`index.html`), the data used for in the examples in Section 5 (`data/`), the package source (`adtoolbox_0.1.0.tar.gz`), and a README.md file containing the install instructions for running the scripts.

### 2025-10-02 index.tex
minor revision

>>>>

\section*{Supplementary material}\label{supplementary-material}
\addcontentsline{toc}{section}{Supplementary material}

The supplementary materials include a full script of the examples in the
paper (\texttt{index.R}) and its output (\texttt{index.html}), the data
used for in the examples in Section 5 (\texttt{data/}), the package
source (\texttt{adtoolbox\_0.1.0.tar.gz}), and a README.md file
containing the install instructions for running the scripts.
